`flippant` --- An `R` package for the automated analysis of fluorescense--based

### 2016-09-11 inst/manuscript/manuscript.rmd
Minor reformatting;

---
title: '`flippant` --- An `R` package for the automated analysis of fluorescense--based
  scramblase assays'
author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon^‡^
  and Johannes Graumann ^†,^*
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  pdf_document:
    fig_caption: yes
  html_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
csl: bioinformatics.csl
bibliography: flippant.bib
---

>>>>

---
title: '`flippant` --- An `R` package for the automated analysis of fluorescense--based
  scramblase assays'
author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon^‡^
  and Johannes Graumann ^†,^*
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  word_document:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
  html_document:
    fig_caption: yes
csl: bioinformatics.csl
bibliography: flippant.bib
---
